\Large \bf TBD

### 2021-09-08 LaTeX-LNCS-2022/sections/paper.tex
added the L2 diagram fig/LissyL2.md)
L2 new hardhat code + numbers + table (text updated as well)

Our proof of concept, \cm, is a call market that will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq} ). Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). \cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC). We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics. Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored. The Solidity source code for \cm and Truffle test files are available in a GitHub repository.\footnote{Github: Link removed for anonymity.} We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}. We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop). Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
Also, \cm is an extensible base class that is still functional without any extensions. Figure\textblue{mindmap} represents a design  landscape and extensions.

@@

% = = = = = = = = = = = = = = = = = = = = = = = = =  %
\subsection{\cm on Arbitrum}

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus, we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Our experiments show that on Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs cost only 1,632 in Layer 1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the Inbox, which is 103 bytes of calldata. As the number of pairs increases, Layer 1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,656.

 % Arbitrum Rinkeby test results:

 % Heap Dynamic Array: 100 order submissions averaged L2 arbgas: 1,659,416, L1 gas: fixed: 2656

 % Linked List w/ Mapping: 100 order submissions averaged L2 arbgas: 2,452,376, L1 gas: fixed: 2656

 % Heap Dynamic Array: worst case matching, 38 pairs of orders: tx hash: 0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01, L1 gas: 1632, L2 arbgas: 1,039,351
 % (https://explorer5.arbitrum.io/#/tx/0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01)

 % Linked List w/ Mapping: worst case matching, 38 pairs of orders: tx hash: 0x96aa143aee7bfb529d35456bef86387ef2adac30f222ea6a3216ded313e00973, L1 gas: 1632, L2 arbgas: 800,529
 % (https://explorer5.arbitrum.io/#/tx/0x96aa143aee7bfb529d35456bef86387ef2adac30f222ea6a3216ded313e00973)

>>>>

Our proof of concept, \cm, is a call market that will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq} ). Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). \cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC). We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics. Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored. The Solidity source code for \cm and Truffle test files are available in a GitHub repository.\footnote{Github: Link removed for anonymity.} We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}. We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop). Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
\textblue{Figuremindmap represents a design  landscape and extensions.}

@@

% = = = = = = = = = = = = = = = = = = = = = = = = =  %
\subsection{\cm on Arbitrum}
\input{tables/performance_Arbitrum}

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus, we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Our experiments show that on Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs cost only 6,569 in Layer 1 gas (a 99.9\% savings). This is effectively the cost of submitting \texttt{closeMarket()} transaction to the inbox and recording the function call, which is 103 bytes of calldata. As the number of pairs increases, Layer 1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 6,917.
